Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-26 paper/paper.Rmd
more &nbsp replacements
spell check

Spatial CV is implemented in the form of leave-one-block-out CV using coordinate-based $k$-means clustering to generate  irregularly shaped blocks of roughly equal size.
This approach is better suited for the irregular shape of the present study area than a rectangular partitioning.
Figures&nbsp;\@ref(fig:vis-spcv-eval)) and&nbsp;\@ref(fig:vis-nspcv-eval)) show the contrasting distributions of training and test samples.
For demonstration purposes we use only four CV folds and two repetitions.

@@

Although the case study example in section \@ref(sec:case-study) used the `"spcv_coords"` method for coordindate-based clustering, this should not give the impression that this method is the only method suitable for this example task.
In this application setting, we want to assess how well the model generalized from the concrete set of historical landslide occurrences, which is why we ensured that training and test sets contain different, "new" hillslopes and landslides.
Coordinate-based clustering is particularly appealing in this setting because of its ability to adapt to the irregularly shaped study area of this example.
Resampling at the level of sub-catchments could have been a viable alternative approach that can be implemented using custom resampling (`"custom_cv"` method); however, this may result in less balanced sizes of test sets as catchment sizes may vary.
When the timing of landslides is known (event-based inventories) or multiple inventories have been compiled for different time points, it can also be recommendable to additionally sample training and test data from different time points, as with the LLTO and LTO [@meyer2018] or similar methods [@brenning2005].

>>>>

Spatial CV is implemented in the form of leave-one-block-out CV using coordinate-based $k$-means clustering to generate  irregularly shaped blocks of roughly equal size.
This approach is better suited for the irregular shape of the present study area than a rectangular partitioning.
Figures \@ref(fig:vis-spcv-eval)) and \@ref(fig:vis-nspcv-eval)) show the contrasting distributions of training and test samples.
For demonstration purposes we use only four CV folds and two repetitions.

@@

Although the case study example in section \@ref(sec:case-study) used the `"spcv_coords"` method for coordinate-based clustering, this should not give the impression that this method is the only method suitable for this example task.
In this application setting, we want to assess how well the model generalized from the concrete set of historical landslide occurrences, which is why we ensured that training and test sets contain different, "new" hillslopes and landslides.
Coordinate-based clustering is particularly appealing in this setting because of its ability to adapt to the irregularly shaped study area of this example.
Resampling at the level of sub-catchments could have been a viable alternative approach that can be implemented using custom resampling (`"custom_cv"` method); however, this may result in less balanced sizes of test sets as catchment sizes may vary.
When the timing of landslides is known (event-based inventories) or multiple inventories have been compiled for different time points, it can also be recommendable to additionally sample training and test data from different time points, as with the LLTO and LTO [@meyer2018] or similar methods [@brenning2005].
